The ground truth is of utmost importance as with machine learning projects.
One major caveat of the VSRG topic is the lack of a ground truth set, thus we create our own.

Ultimately we need a dataset that well describes the population

We can yield 3 important ground truths

\begin{enumerate}
    \item Aggregated Map Difficulty
    \item Time-Series Map Difficulty
\end{enumerate}

\subsection{Aggregated Map Difficulty}\label{subsec:aggregated-map-difficulty}

Upon completing a map, we yield a score describing their performance.
This value is an aggregation of difficulty of the map.
Thus, only provides an aggregated map difficulty feedback.

In order to yield difficulty of specific patterns we need real-time play analysis

\subsubsection*{Methodology}

\begin{enumerate}
    \item Yield the largest score dataset
    \item Filter out anomalies
    \item Predict difficulty of maps
\end{enumerate}

\subsection{Time-Series Map Difficulty}\label{subsec:time-series-map-difficulty}

Using replays of each play, we can evaluate every action in real-time.
This is better suited for pattern difficulty evaluation.

This fine-grained approach will be atomic, though will be more
difficult in every aspect.

\subsubsection*{Methodology}

\begin{enumerate}
    \item Yield Replays using API with \verb+replay_id+ in~\ref{subsec:aggregated-map-difficulty}
    \item Emulate Replays to find errors in plays
    \item Decompose Map into Patterns
    \item Link errors to patterns
    \item Predict pattern difficulty
\end{enumerate}